---
title: "Report"
params:
  # LE
  life: NA
  continents: NA
  # GDP
  gdp: NA
  continents_gdp: NA
  # POP
  continents_pop: NA
  pop: NA
  # Population Growth
  country: Na
  year: NA
  future_pop: NA
output:
  html_document:
    code_folding: "hide"
    #self_contained: true
    theme: spacelab
    highlight: tango
    toc: true
    toc_float: false
---
```{r include = FALSE}
knitr::opts_chunk$set(echo=FALSE,error = F, warning = F, message = F)
```
```{r}
library(dplyr)
library(shiny)    # for shiny apps
library(leaflet)  # renderLeaflet function
library(spData)   # loads the world dataset 
library(sf)
library(shinydashboard)
library(shinyWidgets)
library(kableExtra)
world$`lifeExp` = round(world$`lifeExp`, 2)  
world$`gdpPercap` = round(world$`gdpPercap`)
world$`pop` = round(world$`pop`)

world = world %>% 
    left_join(worldbank_df, by = "iso_a2") %>%
    select(name_long, pop, gdpPercap, pop_growth, continent, lifeExp)
```

**Report generated on  `r format(Sys.Date(), '%d-%m-%Y')`**

# 1. Life expectancy

In Figure 1, we can see the average life expectancy in the world. 
Table 1 displays the average Life Expectancy values for the selected range *`r params$life`*


```{r, fig.align = 'center', fig.cap = 'Figure 1. Life expectancy'}
labels <- sprintf(
            "<strong>%s</strong><br/>%g",
            world$name_long, world$lifeExp
        ) %>% lapply(htmltools::HTML)

        bins <- c(40, 50, 60, 70, 75, 80, Inf)
        pal <- colorBin("Blues", domain = world$lifeExp, bins = bins)

        lifeExp_map <- leaflet(world) %>%
            addProviderTiles("Stamen.Toner")

        lifeExp_map %>%
            addPolygons(
                fillColor = ~pal(lifeExp),
                weight = 2,
                opacity = 3,
                color = "white",
                dashArray = "1",
                fillOpacity = 1.2,
                highlight = highlightOptions(
                    weight = 2,
                    color = "blue",
                    fillOpacity = 0.7),
                label = labels,
                labelOptions = labelOptions(
                    style = list("font-weight" = "normal", padding = "2px 6px"),
                    textsize = "10px")) %>%
            addLegend(pal = pal, values = ~lifeExp, opacity = 0.7, position = "bottomright")
```

```{r}
dane= world %>%
            filter(
                continent %in% params$continents,
                lifeExp > params$life[1],
                lifeExp < params$life[2]
            ) %>%
            select(name_long, lifeExp) %>%
            arrange(desc(lifeExp))
kable(dane, align = "cc", caption = "Table 1. Life expectancy") %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


# 2. GDP

In Figure 2, we can see the GDP values for individual countries.
Table 2 displays GDP for the selected range *`r params$gdp`*

```{r, fig.align = 'center', fig.cap = 'Figure 2. GDP'}
labels <- sprintf(
            "<strong>%s</strong><br/>%g US dollars per capita",
            world$name_long, world$gdpPercap
        ) %>% lapply(htmltools::HTML)

        bins <- c(0, 1000, 5000, 10000, 25000, 45000, Inf)
        pal <- colorBin("Greens", domain = world$gdpPercap, bins = bins)

        gdp_map <- leaflet(world) %>%
            addProviderTiles("Thunderforest.Pioneer")

        gdp_map %>%
            addPolygons(
                fillColor = ~pal(gdpPercap),
                weight = 2,
                opacity = 3,
                color = "white",
                dashArray = "1",
                fillOpacity = 1.2,
                highlight = highlightOptions(
                    weight = 2,
                    color = "blue",
                    fillOpacity = 0.7),
                label = labels,
                labelOptions = labelOptions(
                    style = list("font-weight" = "normal", padding = "2px 6px"),
                    textsize = "10px")) %>%
            addLegend(pal = pal, values = ~gdpPercap, opacity = 0.7, position = "bottomright")
```

```{r}
dane= world %>%
            filter(
                continent %in% params$continents_gdp,
                gdpPercap > params$gdp[1],
                gdpPercap < params$gdp[2]
            ) %>%
            select(name_long, gdpPercap, pop) %>%
            arrange(desc(gdpPercap))
kable(dane, align = "cc", caption = "Table 2. GDP") %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

# 3. Population

#### {.tabset}
##### pop

In Figure 3, we can see the population for each country.

```{r, fig.align = 'center', fig.cap = 'Figure 3. Population'}
world$pop = world$pop / 1000000 # To present population in milions on map
world$pop = round(world$pop, 3)
        
        # setting map options
        
        labels <- sprintf(
            "<strong>%s</strong><br/>%g milion people",
            world$name_long, world$pop
        ) %>% lapply(htmltools::HTML)
        bins <- c(0, 1, 10, 25, 50, 200, Inf)
        pal <- colorBin("YlOrRd", domain = world$pop, bins = bins)
        
        # plotting map
        
        gdp_map <- leaflet(world) %>%
            addProviderTiles("Stamen.Toner")
        
        gdp_map %>% 
            addPolygons(
                fillColor = ~pal(pop),
                weight = 2,
                opacity = 3,
                color = "white",
                dashArray = "1",
                fillOpacity = 1.2,
                highlight = highlightOptions(
                    weight = 2,
                    color = "blue",
                    fillOpacity = 0.7),
                label = labels,
                labelOptions = labelOptions(
                    style = list("font-weight" = "normal", padding = "2px 10px"),
                    textsize = "10px")) %>%
            addLegend(pal = pal, values = ~pop, opacity = 0.7, position = "bottomright", title = 'Population in millions')
```

##### Population Growth

```{r}
future_pop <- function(country, year) {
    
    if (year <= 2021)
        "The value of year inputted must be greater than current year!"
    else if (country %in% world$name_long == F)
        "The name of the country not found!"
    else {
        pop = world$pop[world$name_long == country][1]
        pop_growth = world$pop_growth[world$name_long == country][1]
        final_pop = pop * compoundInterest((pop_growth/100), (year-2021))
        cat(country, "would have", final_pop, "people if it's going to grow at the current rate of", round(pop_growth, 2), "% per year")
    }
}
a = future_pop(params$country, params$year)
```

*`r print(a)`*

```{r, fig.align = 'center', fig.cap = 'Figure 4. Population Growth'}
library(ggplot2)
library(dplyr)

thismap = map_data("world")
thismap <- mutate(thismap, fill = ifelse(region %in% c(params$country), "red", "white"))

ggplot(data = thismap, aes(long, lat, fill = fill, group=group))+ 
  geom_polygon(colour="darkgray") + 
  scale_fill_identity()
        
```
Information about selected country:

```{r}
library(WikipediR)
library(rvest)
wp_content <- page_content("en","wikipedia", page_name = params$country)
a= read_html(wp_content$parse$text$`*`) %>% html_node('body div') %>% html_text()
a =gsub('\n', '', a)
a = a %>% as.character()
```

`r substr(a, 1, 100)`
------------------------------------------------------------------------------------
Source: ["wikipedia.org"](https://www.wikipedia.org/)

